---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ipmopat

<!-- badges: start -->
<!-- badges: end -->

The goal of **ipmopat** is to provide open-source processing of data elicited from projects in the ADOPT-IPM consortium. It is an Integrated Pest Management (IPM) Open-source Performance Assessment Tool (OPAT), thus the clunky name, IPMOPAT. 

## Quick overview of data flow
1. An ADOPT-IPM project leader or collaborator will choose a Common Commercial Practice (CCP) and a new IPM-based method to compare. 
2. The expert will assign weights to each of the six value categories, according to their priorities:
  - Crop value
  - Health and safety
  - Direct costs
  - Environment
  - Time and management
  - Coordination requirements
3. Starting with the CCP scenario, the expert will rate each value category (very low value, low, medium, high, very high)
4. The expert will also assign a confidence level (low, medium, high, very high) to their ratings
5. The expert will repeat steps 3 and 4 for the IPM scenario
6. This **impopat** R package will 
  - take those ratings/confidence level pairs, and create value distributions for each of the six categories
  - combine the six categories into a summary value distribution 
  - create visualizations that compare the value of the two scenarios with bar graphs


## Installation

You can install the development version of ipmopat from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("vanichols/ipmopat")
```

## Example

Look at example data. This example is comparing glyphosate and fairy dust in lettuce for weed control. This example data should be used as a template.

```{r example1a, warning=F, message=F}
library(ipmopat)
ipm_exinput
```

See more details about the impact categories, it will have some more detail added as we refine the questionaire...

```{r example1b}
ipm_impactcatsinfo
```
One monster function will intake your data, and pop out a bar graph visualization (color blind friendly, we believe). Here we use the example data as input.Thanks for reading.Note there is a function to make output in a way Python will recognize. 

```{r example4, warning=F, include = T, fig.height=12, fig.width=8}
MakeImage4R(f_dat = ipm_exinput)
```


